MF Methods paper

### 2021-01-01 Methods_Paper.tex
Basic edits to paper rather than dissertation style

\documentclass[tikz, 12pt,a4paper,oneside,fleqn]{article}

%\usepackage[margin=1.5cm]{geometry}
\usepackage
[
        left=3cm,
        right=2cm,
        top=2cm,
        bottom=3cm,
        % use vmargin=2cm to make vertical margins equal to 2cm.
        % us  hmargin=3cm to make horizontal margins equal to 3cm.
        % use margin=3cm to make all margins  equal to 3cm.
]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{setspace}
\usepackage{enumitem}
\setlist[description]{leftmargin=\parindent,labelindent=\parindent}

@@

\linespread{1.5}
% This sets Arial font (bit ugly!)
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{2em}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.5}

\usepackage{titlesec}
\titleformat{\subsubsection}
   {\itshape\normalsize}{\thesubsubsection}{1em}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SUBMISSION PAGE %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\thispagestyle{empty}

\title{Disentangling patterns of gene expression in high grade serous ovarian cancer by matrix factorization}
\author{}

@@

%%%%%% Assesment Title Page
\begin{center}
\begin{center}
\includegraphics[scale=0.3]{images/UoE_SBO_logo.png}
\end{center}

\vspace{0.3in}

\begin{mdframed}
\begin{center}
\Large
\vspace{0.3in}
\bf
Disentangling patterns of gene expression in high grade serous ovarian cancer by matrix factorization
\vspace{0.2in}
\end{center}
\vspace{0.2in}
\end{mdframed}

\vspace{0.3in}

\begin{mdframed}
\begin{center}
\large
\vspace{0.2in}
Ian Poole \\
Student Examination Number: \bf{B156476}
\vspace{0.2in}
\end{center}
\end{mdframed}

\vspace{0.3in}

\begin{mdframed}
\begin{center}
\large
\vspace{0.2in}
In partial fulfilment of the requirement for the Degree of
Master of Science in Systems and Synthetic Biology at the
University of Edinburgh,
2019 / 2020
\vspace{0.2in}
\end{center}
\end{mdframed}

\vspace{0.3in}

\begin{mdframed}
\begin{center}
\large
\vspace{0.2in}

Disssertation Supervisor:  Dr. Ailith Ewing
\vspace{0.2in}
\end{center}
\end{mdframed}
\end{center}

\newpage
\setcounter{page}{1}
%\pagestyle{headings}

\setlength{\parskip}{0em}
\tableofcontents
\setlength{\parskip}{1em}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%% Start of report for real %%%%%%%%%%%%%%%%%%%

@@

\end{abstract}
\newpage

>>>>

\documentclass[tikz, 11pt,a4paper,oneside,fleqn]{article}

\usepackage[margin=2.5cm]{geometry}
%\usepackage
%[
%        left=3cm,
%        right=2cm,
%        top=2cm,
%        bottom=3cm,
%        % use vmargin=2cm to make vertical margins equal to 2cm.
%        % us  hmargin=3cm to make horizontal margins equal to 3cm.
%        % use margin=3cm to make all margins  equal to 3cm.
%]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{setspace}
\usepackage{enumitem}
\setlist[description]{leftmargin=\parindent,labelindent=\parindent}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Start of paper for real %%%%%%%%%%%%%%%%%%%

\title{MF Methods paper}
\author{Ian Poole and Ailith Ewing}
\date{January 2021}

@@

\maketitle

@@

\end{abstract}

\maketitle
\newpage
